Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2023-03-10 Thesis/chapter/063-discussion.tex
sation to zation

\section{Hindsight is easier than foresight}
%\section{Discussion}
%\todo{search i.e. and replace with i.e.\ }
%\todo{go to experimental and material (IV) discussion}
%\td{I-V: 2 terminal measurement one terminal was varibale and the other the ground from $-5*10^{-3}$ V to $5*10^{-3}$ V with steps of $10^{-2}$ measure current from back bone to backbone if shorted, then can measure actual resistance of layer. resistance of steel is neglectable. In order to get an impression of the quality of the layer mutliple contact (picture) are sputtered (throuhg a mask) and statistics: Two angabewerte: the weighted durchschnit and the number of pinholes, ie the number of contacts which were shorted, have an resistance below an threshold. if tunneling, iv follows powerlaw, if direct contact, iv follows linear }
%\todo{go to anova discussion}
%- \td{The disadvantage of ANOVA is that information is lost because independent variables are assumed categorical even though they are ordinal}
%\todo{british or US?: sation vs zation} 
%\todo{ include last phase into previous section}
This section will discuss mistakes, improvements and lessons learned for each phase of this project in chronological order. 
Firstly, the 
\ref{sec:phase1} \textit{\nameref{sec:phase1}}%
, followed by the 
\ref{sec:phase2} \textit{\nameref{sec:phase2}}%
%, thereupon the 
 and finally the 
\ref{sec:phase3} \textit{\nameref{sec:phase3}}%
%\ref{sec:phase3} \textit{\nameref{sec:phase4}}%
 will be discussed.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Research, exploration and design phase}
\label{sec:phase1}
%\td{freewriting}: 
\textbf{Scrutinize everything!} At the beginning of a project it is important 
to get a ``feel''. I took the first recipe as only true recipe and tried to tune it to perfection. 
The problem was that the base line of that recipe was so low such that no matter how much I improved it, it was still bad. 
I only noticed this after trying out another recipe. 
My tip here is to read as much and mostly diverse literature as possible and then try to mimic what ever you can. 
This will get you a ``feel'' of what works and what does not. 
Thinking back to some design classes I took for data visualization: create as many and different designs as possible. 
Check what works, collect (dis-)advantages of methods and combine the best approaches. 
This can save you a lot of time.

Moreover, it is important to define the objective of the project as clear and unambiguous as possible. 
Again, try to reformulate the objective in multiple ways and choose the most fitting. 
Answer which question should be answered, and establish hypotheses with corresponding null hypotheses. 
A general experimental design procedure was stated by Cherkassky and Mulier in  ``Learning from Data''\cite{cherkassky1998learning}:
\begin{enumerate}
    \item {State the problem}
    \item {Formulate the hypothesis}
    \item {Design the experiment/data generation process}
    \item {Collect the data and perform preprocessing}
    \item {Estimate the model}
    \item {Interpret the model/draw the conclusion}
\end{enumerate}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Narrowing, pre-optimisation and constraint phase}
\label{sec:phase2}
The selection of input and output variables, data encoding/representation and incorporating a prior knowledge into the design of the learning system is often more critical for an overall success than the design of the learning machine itself.\cite{cherkassky1998learning} %(page 25)
After having decided on a base recipe, it is important to define limits and decrease the number of independent variables. 
The later is more important due to the curse of dimensionality\cite{cherkassky1998learning}, 
which states that with increasing dimensionality it get exponentially more difficult to arrive at the same density of data points. 
By excluding input variables from the model, 
the complexity of the model can be drastically reduced. 
This leads to more information which can be extracted from the remaining data, 
be it in more detail of the dependence or higher confidence interval. 
A good measure to compare with literature and other methods is the \gls{epv}. 
The \gls{epv} in this work is round 5,
which is low in comparison with literature consulted
\cite{
ahmed2017preparation,
fernandes2010multi,
kaczmarowski2015genetic,
mahdavi2017hardness,
soltanali2014neural,
panwar2014design,
schubert2008design,
shanaghi2013experimental}.
Reducing variables is of course no easy task.
How does one decide which variables to keep and which to incorporate into the model and which to discard? 
There is an intuitive (expert) way and a mathematical way.
An expert would decide which variables to discard by his expert knowledge about the domain. 
Mathematical ways include principal component analysis and step-wise regression.
%
Additionally, having wide limits can be an advantage when the data is noisy and the dependence is not too complicated, because by moving samples to the boundaries of the design space, the effect of the noise is reduced\cite{giunta2003overview}. 
This suggest variable reduction favorable over limit narrowing.
%"By moving the samples to the boundaries of the design space, the effect of the random term is reduced\cite{giunta2003overview}."
%
There are two opposing principles which should be kept in mind when reducing variables, though:
By introducing a lot of variables into a model presupposes that they and their interactions (!) have a statistically significant effect\cite{gunst2009fractional}.
On the other hand a model can be used to tell if a variable exerts an influence\cite{haertler2014statistisch}. 
%
%One regime where overfitting occurs is when there are to many parameters to be fitted with not enough data. 
Another reason to avoid too many variables in a model is that they introduce more parameters to fit and overfitting happens in the regime where to many parameters are fitted with not enough data.
%todo{Overfitting happens in the regime where to many parameters are fitted with not enough data. }

Another step/deed which is well placed in this phase is the estimate the error by reproducing a single sample a certain number of times. 
%Where the number will then be higher than during optimisation 
%\todo{include curse of dimensionality.}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Optimisation, modelling and data generation}
\label{sec:phase3}
During the optimisation the main problems were too many in- and output variables, reproducibility and regularisation. 
%The first problem 
Variable selection has already been discussed in the previous section. 
When working with stochastic algorithms it is especially important to introduce reproducibility via a seed, which determines all subsequent pseudo-random numbers. 
Finally, during the \gls{emma} optimisation the input data were not regularized, %es wurde auf regularisation verzichtet, 
because the regularization would be different for different generations.
Regularizing with the mean and standard deviation would be either inconsistent across generations or over overvalue the distribution of the initial generation. 
%because the distribution of 
%
%alter previous measurements, which alread beitragen to the model and the influence the decision of the next sample. 
These were the reasons for not including regularization during \gls{emma} optimization. 
On the other hand the input data could have been regularized to only take values $[-1;1]$ by defining the regularized varible as 
$x'= \frac{x-\bar{x}}{x_{max} - \bar{x}}$ with $\bar{x}= x_{\text{max}} - x_{\text{min}}$.
%On the other hand haette man auf jeden fall die input variablen normieren können. 
%Normally, for standardisation the mean is substracted and it is devided by the standard deviation, which impplies a distribution of a random variable. 
%One could have assumed a standard uniform distribution. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55
\iffalse
\begin{itemize}
    \item regularization
    \item reproducability (random in code and repeat sample)
    \item main problems too many in and output vars
%\td{two main problems: 1. too many input variables; 2. too many output varibales; at2: as some input variables were also output variables, MARS couldnt find correct BFs. This could be used though: use input var also as output var if you think they are inportant, this way they will be more likely to be choosen in basis function}
\end{itemize}
\fi
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\iffalse
\subsection{Evaluation, interpretation and outlook phase}
\label{sec:phase4}
\begin{itemize}
    \item why lowest $\gamma$ for lowest $T_{cal}$? according which eq? emma? 
    \item why $\gamma ~ \lambda$? (minimum for layer count?) according which eq? emma? 
    \item reasons for large error per sample: ageing of solution, varying humidity, varying room temperature?, impurities in solutions, inhomogeneity of film, measureing error, systematical/thinking error? what else? 
%What is the reason for aging (O2,H2O?, not sealing accelerates) ? 
%Why does \gls{ipo} decelerate the aging process? ( ipo fits better to solvent(buoh)?)
%the original solvent was 2-methoxy-ethonanol instead of \ch{buoh}.
%\td{COMMENT: solution age was not accounted for}
    \item \td{maybe the lowering of G and p are not because of better process variables but because of me getting better at creating the layers *sad* :0 } 
\end{itemize}
\fi

@@

    \item Dimension reduction bietet sich stark an bei solcher Datenlage. in pre-optimisation!

@@

    \item \textbf{pre-optimisation}{The primary goal of a screening experiment is to identify the active factors. A secondary goal is to provide a simple model that captures the essential features of the relationship between these active factors and the response—that is, to identify the active effects. \cite{miller2001using}} But $2^6=64$ are too many for preliminary test so maybe check base and from there do $2\cdot6=12$ experiments. Then focus on selected input vars, which might have mutliple maxima \\ \td{pre optimization was used to check if limits where okay, but could also have been used to sieve out factors without impact on response (see miller 2001 \cite{miller2001using} section 1) }

@@

>>>>

\section{Hindsight is easier than foresight}
%\section{Discussion}
%\todo{search i.e. and replace with i.e.\ }
%\todo{go to experimental and material (IV) discussion}
%\td{I-V: 2 terminal measurement one terminal was varibale and the other the ground from $-5*10^{-3}$ V to $5*10^{-3}$ V with steps of $10^{-2}$ measure current from back bone to backbone if shorted, then can measure actual resistance of layer. resistance of steel is neglectable. In order to get an impression of the quality of the layer mutliple contact (picture) are sputtered (throuhg a mask) and statistics: Two angabewerte: the weighted durchschnit and the number of pinholes, ie the number of contacts which were shorted, have an resistance below an threshold. if tunneling, iv follows powerlaw, if direct contact, iv follows linear }
%\todo{go to anova discussion}
%- \td{The disadvantage of ANOVA is that information is lost because independent variables are assumed categorical even though they are ordinal}
%\todo{british or US?: zation vs zation} 
%\todo{ include last phase into previous section}
This section will discuss mistakes, improvements and lessons learned for each phase of this project in chronological order. 
Firstly, the 
\ref{sec:phase1} \textit{\nameref{sec:phase1}}%
, followed by the 
\ref{sec:phase2} \textit{\nameref{sec:phase2}}%
%, thereupon the 
 and finally the 
\ref{sec:phase3} \textit{\nameref{sec:phase3}}%
%\ref{sec:phase3} \textit{\nameref{sec:phase4}}%
 will be discussed.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Research, exploration and design phase}
\label{sec:phase1}
%\td{freewriting}: 
\textbf{Scrutinize everything!} At the beginning of a project it is important 
to get a ``feel''. I took the first recipe as only true recipe and tried to tune it to perfection. 
The problem was that the base line of that recipe was so low such that no matter how much I improved it, it was still bad. 
I only noticed this after trying out another recipe. 
My tip here is to read as much and mostly diverse literature as possible and then try to mimic what ever you can. 
This will get you a ``feel'' of what works and what does not. 
Thinking back to some design classes I took for data visualization: create as many and different designs as possible. 
Check what works, collect (dis-)advantages of methods and combine the best approaches. 
This can save you a lot of time.

Moreover, it is important to define the objective of the project as clear and unambiguous as possible. 
Again, try to reformulate the objective in multiple ways and choose the most fitting. 
Answer which question should be answered, and establish hypotheses with corresponding null hypotheses. 
A general experimental design procedure was stated by Cherkassky and Mulier in  ``Learning from Data''\cite{cherkassky1998learning}:
\begin{enumerate}
    \item {State the problem}
    \item {Formulate the hypothesis}
    \item {Design the experiment/data generation process}
    \item {Collect the data and perform preprocessing}
    \item {Estimate the model}
    \item {Interpret the model/draw the conclusion}
\end{enumerate}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Narrowing, pre-optimization and constraint phase}
\label{sec:phase2}
The selection of input and output variables, data encoding/representation and incorporating a prior knowledge into the design of the learning system is often more critical for an overall success than the design of the learning machine itself.\cite{cherkassky1998learning} %(page 25)
After having decided on a base recipe, it is important to define limits and decrease the number of independent variables. 
The later is more important due to the curse of dimensionality\cite{cherkassky1998learning}, 
which states that with increasing dimensionality it get exponentially more difficult to arrive at the same density of data points. 
By excluding input variables from the model, 
the complexity of the model can be drastically reduced. 
This leads to more information which can be extracted from the remaining data, 
be it in more detail of the dependence or higher confidence interval. 
A good measure to compare with literature and other methods is the \gls{epv}. 
The \gls{epv} in this work is round 5,
which is low in comparison with literature consulted
\cite{
ahmed2017preparation,
fernandes2010multi,
kaczmarowski2015genetic,
mahdavi2017hardness,
soltanali2014neural,
panwar2014design,
schubert2008design,
shanaghi2013experimental}.
Reducing variables is of course no easy task.
How does one decide which variables to keep and which to incorporate into the model and which to discard? 
There is an intuitive (expert) way and a mathematical way.
An expert would decide which variables to discard by his expert knowledge about the domain. 
Mathematical ways include principal component analysis and step-wise regression.
%
Additionally, having wide limits can be an advantage when the data is noisy and the dependence is not too complicated, because by moving samples to the boundaries of the design space, the effect of the noise is reduced\cite{giunta2003overview}. 
This suggest variable reduction favorable over limit narrowing.
%"By moving the samples to the boundaries of the design space, the effect of the random term is reduced\cite{giunta2003overview}."
%
There are two opposing principles which should be kept in mind when reducing variables, though:
By introducing a lot of variables into a model presupposes that they and their interactions (!) have a statistically significant effect\cite{gunst2009fractional}.
On the other hand a model can be used to tell if a variable exerts an influence\cite{haertler2014statistisch}. 
%
%One regime where overfitting occurs is when there are to many parameters to be fitted with not enough data. 
Another reason to avoid too many variables in a model is that they introduce more parameters to fit and overfitting happens in the regime where to many parameters are fitted with not enough data.
%todo{Overfitting happens in the regime where to many parameters are fitted with not enough data. }

Another step/deed which is well placed in this phase is the estimate the error by reproducing a single sample a certain number of times. 
%Where the number will then be higher than during optimization 
%\todo{include curse of dimensionality.}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Optimization, modelling and data generation}
\label{sec:phase3}
During the optimization the main problems were too many in- and output variables, reproducibility and regularization. 
%The first problem 
Variable selection has already been discussed in the previous section. 
When working with stochastic algorithms it is especially important to introduce reproducibility via a seed, which determines all subsequent pseudo-random numbers. 
Finally, during the \gls{emma} optimization the input data were not regularized, %es wurde auf regularization verzichtet, 
because the regularization would be different for different generations.
Regularizing with the mean and standard deviation would be either inconsistent across generations or over overvalue the distribution of the initial generation. 
%because the distribution of 
%
%alter previous measurements, which alread beitragen to the model and the influence the decision of the next sample. 
These were the reasons for not including regularization during \gls{emma} optimization. 
On the other hand the input data could have been regularized to only take values $[-1;1]$ by defining the regularized varible as 
$x'= \frac{x-\bar{x}}{x_{max} - \bar{x}}$ with $\bar{x}= x_{\text{max}} - x_{\text{min}}$.
%On the other hand haette man auf jeden fall die input variablen normieren können. 
%Normally, for standardization the mean is substracted and it is devided by the standard deviation, which impplies a distribution of a random variable. 
%One could have assumed a standard uniform distribution. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55
\iffalse
\begin{itemize}
    \item regularization
    \item reproducability (random in code and repeat sample)
    \item main problems too many in and output vars
%\td{two main problems: 1. too many input variables; 2. too many output varibales; at2: as some input variables were also output variables, MARS couldnt find correct BFs. This could be used though: use input var also as output var if you think they are inportant, this way they will be more likely to be choosen in basis function}
\end{itemize}
\fi
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\iffalse
\subsection{Evaluation, interpretation and outlook phase}
\label{sec:phase4}
\begin{itemize}
    \item why lowest $\gamma$ for lowest $T_{cal}$? according which eq? emma? 
    \item why $\gamma ~ \lambda$? (minimum for layer count?) according which eq? emma? 
    \item reasons for large error per sample: ageing of solution, varying humidity, varying room temperature?, impurities in solutions, inhomogeneity of film, measureing error, systematical/thinking error? what else? 
%What is the reason for aging (O2,H2O?, not sealing accelerates) ? 
%Why does \gls{ipo} decelerate the aging process? ( ipo fits better to solvent(buoh)?)
%the original solvent was 2-methoxy-ethonanol instead of \ch{buoh}.
%\td{COMMENT: solution age was not accounted for}
    \item \td{maybe the lowering of G and p are not because of better process variables but because of me getting better at creating the layers *sad* :0 } 
\end{itemize}
\fi

@@

    \item Dimension reduction bietet sich stark an bei solcher Datenlage. in pre-optimization!

@@

    \item \textbf{pre-optimization}{The primary goal of a screening experiment is to identify the active factors. A secondary goal is to provide a simple model that captures the essential features of the relationship between these active factors and the response—that is, to identify the active effects. \cite{miller2001using}} But $2^6=64$ are too many for preliminary test so maybe check base and from there do $2\cdot6=12$ experiments. Then focus on selected input vars, which might have mutliple maxima \\ \td{pre optimization was used to check if limits where okay, but could also have been used to sieve out factors without impact on response (see miller 2001 \cite{miller2001using} section 1) }

@@

\td{when adding dep var to model this has two folgen: - beeinflusst the BF and the optimization, but bcs relatiev weight is only 0.05 for each, no big beeinflussung on optimization}

### 2023-03-10 Thesis/chapter/07-outlook.tex
sation to zation

%\todo{freewriting:} 
%what did i want to do? 
The goal of this work was to find a sol-gel doctor blading process resulting in a insulating zirconium ceramic on top of steel.
This structure then can be used as substrate for thin layer photo voltaics. 
The ceramic needs to be homoegeneous and defect free in order to insulate properly.
%what was done? 
A suitable recipe was found\cite{Hu2016} and the process variables were optimized via \gls{emma}. 
The recipe was improved by increasing its stability. 
The best parameters found by the emma optimisation were 
$c_{zr}=2$, $\lambda=10$, $v_{DB}=10$, $T_{DB}=40$, $v_{cal}=120$ and $T_{cal}=300$.
%\todo{$T_{cal}=300$}. 
%welche methoden wurden dafür verwendet? 
After optimsation the data was analysed with further machine learning methods like kernel ridge regression, support vector regression and linear regression. 
The comparisson of methods showed that \gls{emma} performed well on predicting the correlation between conductance and process variables. 
%was wurde herausgefunden? 
A strong correlation of calcination temperature and conductance in the bereich of 300--400\oc{}. 
%was kann noch herausgefundne werden und wie? 
Next steps include to investigate if the correlation of condactance and calcination temperature are statistically significant or due to small sample size. 
The aging process could be examined via infra red spectroscopy. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\iffalse
was kann noch veraendert werden? 
humidity 
solution age
vdb and tdb on g and phd 
Tcal on g and phd 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5

>>>>

%\todo{freewriting:} 
%what did i want to do? 
The goal of this work was to find a sol-gel doctor blading process resulting in a insulating zirconium ceramic on top of steel.
This structure then can be used as substrate for thin layer photo voltaics. 
The ceramic needs to be homoegeneous and defect free in order to insulate properly.
%what was done? 
A suitable recipe was found\cite{Hu2016} and the process variables were optimized via \gls{emma}. 
The recipe was improved by increasing its stability. 
The best parameters found by the emma optimization were 
$c_{zr}=2$, $\lambda=10$, $v_{DB}=10$, $T_{DB}=40$, $v_{cal}=120$ and $T_{cal}=300$.
%\todo{$T_{cal}=300$}. 
%welche methoden wurden dafür verwendet? 
After optimzation the data was analysed with further machine learning methods like kernel ridge regression, support vector regression and linear regression. 
The comparisson of methods showed that \gls{emma} performed well on predicting the correlation between conductance and process variables. 
%was wurde herausgefunden? 
A strong correlation of calcination temperature and conductance in the bereich of 300--400\oc{}. 
%was kann noch herausgefundne werden und wie? 
Next steps include to investigate if the correlation of condactance and calcination temperature are statistically significant or due to small sample size. 
The aging process could be examined via infra red spectroscopy. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\iffalse
was kann noch veraendert werden? 
humidity 
solution age
vdb and tdb on g and phd 
Tcal on g and phd 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
